\documentclass[14pt]{article}
\usepackage{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\begin{document}

Possible questions regarding the airport flight data:

\begin{enumerate}

\item Is there any evidence that airlines have been increasingly padding their flight duration times to avoid the appearance of flight delays? Please examine this using 25 years of flight data for the entire country.

\item Are there any airlines with flight delays that are systematically worse than other airlines? Please examine this using 25 years of flight data for the entire country.

\item Are there any airports with flight departure delays that are systematically worse (or better) than other airports? Be sure to consider seasonal fluctuations that might be due to differential weather patterns, using 25 years of flight data for the entire country.

\item What time of day and day of week are best for avoiding flight delays? Use 25 years of flight data for the entire country.

\item Are there any airlines that have shown consistent improvement in flight delays, across the entire country, over the 25 years of flight data?

\item Are there geographical patterns in weather-related flight delays, and do these change over time. Use 25 years of flight data for the entire country.

\end{enumerate}

Some possible readings: \vspace*{.5in}

\begin{itemize}

\item \textcolor{blue}{\href{http://www.ft.com/cms/s/2/21a6e7d8-b479-11e3-a09a-00144feabdc0.html#axzz2zqWDPG2I}{Big Data: are we making a big mistake?}}

\item \textcolor{blue}{\href{http://datacommunitydc.org/blog/2014/03/will-big-data-bring-return-sampling-statistics-review-aaron-strausss-talk-dsdc/}{Return of Sampling Statistics}}

\end{itemize}

\end{document}
